---
title: "Nascar Tire Report"
author: "F. T .M. McKay, Data Scientist"
date: "`r format(Sys.Date(),'%A, %B %d, %Y')`"
description:  >
  Template for creting an article for submission to RPubs
output: 
  ioslides_presentation:
    logo:  C:\RepTemplates\PeerGradedAssignment\images\nascar2.jpeg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Abstract

This is an R Markdown presentation required to complete a peer graded assignment, the details of which follow on the next slide. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Required Items for Assignment Complete

- Four Items Above (Title, Author, Date, Presentation Summary/Template Description) 
- This Bulleted List (3 or More Items, Numbered or Unnumbered)
- Plotting of Built-In 'pressure' Dataset
- Table of top 6 rows of the Built-In 'cars' Dataset
- All Knit to HTML with Custom Theme and Published to RPubs

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```



